On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-02-01 docs/mvfits_paper/mvf.tex
adding more to response to second ref

In the second line, the equality has been replaced by an approximation as we have limited the linear representation to $K$ terms.

@@

    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product of the power set of each basis symbol

@@

Each term is an element of the $n$-fold cartesian inner-product of the power-sets of each model dimension. That is $\mlam_{bulk} = \{x_0,x_1 .. x_N, ... x_0^1, x_0^2, x_0^3, ...  , (x_0^K x_1^K ... x_N^K) \}$.

@@

	\caption{ Standard summary plot for Greedy Multivariate Rational fitting algorithm (\gmvr) as implemented in \cite{lionel_london_2018_1402516}. (\textit{left}) 3D plot of training data (black dots) and final fit (red mesh). (\textit{center top}) Same as left most panel, but in index space. (\textit{center bottom}) Fractional residual error (grey blocks) along with uniform (black) and gaussian (red) fits to error. (\textit{top right}) convergence of the L2 norm during iterative refinement. (\textit{bottom right}) Same as top right, but on log scale, where $\epsilon_0$ is the value of $\epsilon$ at the final $k^{\mathrm{th}}$ iteration of refinement. }

@@

\par To generate the test data, \eqn{eq:gmvrtoy1} is evaluated with 25 points in $x_0$ and $x_1$, where each is between -3 and 3. Though not a requirement of \gmvr{}, for simplicity of presentation, domain points are equally spaced.

@@

\fig{fig:gmvrtoy}'s central bottom panel displays the distribution of fractional residuals, and demonstrates their approximately flat distribution.

@@

Specifically, when considering many noise realizations, we find that sample noise and residuals have an average correlation of $99.46\%$.

@@

\par Lastly, \fig{fig:qnm}'s bottom two panels show fractional residual errors.

@@

Although each model's fractional error is within 2\%, each error is dominated by well known nonlinear oscillations which are considered to be outside of the experimental accuracy of current 2nd generation \gw{} efforts.

@@

    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product of the power set of each basis symbol. This is the combined bulk for numerator and denominator symbols.

>>>>

In the second line, the equality has been replaced by an approximation as we have limited the linear representation to $K+1$ terms.

@@

    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product (i.e. tensor product) of the power set of each basis symbol

@@

Each term is an element of the tensor-product of the power-sets of each model dimension. That is $\mlam_{bulk} = \{x_0,x_1 .. x_N, ... x_0^1, x_0^2, x_0^3, ...  , (x_0^K x_1^K ... x_N^K) \}$.

@@

	\caption{ Standard summary plot for Greedy Multivariate Rational fitting algorithm (\gmvr) as implemented in \cite{lionel_london_2018_1402516}. (\textit{left}) 3D plot of training data (black dots) and final fit (red mesh). (\textit{center top}) Same as left most panel, but in index space. (\textit{center bottom}) {Percent residual error with respect to validation data (grey blocks) along with uniform (black) and gaussian (red) fits to error. The validation data were generated in the same manner as the training data.} (\textit{top right}) convergence of the L2 norm during iterative refinement. (\textit{bottom right}) Same as top right, but on log scale, where $\epsilon_0$ is the value of $\epsilon$ at the final $k^{\mathrm{th}}$ iteration of refinement. }

@@

\par To generate the test data, \eqn{eq:gmvrtoy1} is evaluated with 25 points along $x_0$ and $x_1$ (with $25^2$ total points), where each is between -3 and 3. Though not a requirement of \gmvr{}, for simplicity of presentation, domain points are equally spaced.

@@

\fig{fig:gmvrtoy}'s central bottom panel displays the distribution of percentage residuals with respect to validation data generated in the same manner as training data.

@@

Moreover, when considering many noise realizations to generate validation data, we find that sample noise and residuals have an average correlation of $99.46\%$.

@@

\par Lastly, \fig{fig:qnm}'s bottom two panels show absolute fractional residual errors of the complex frequency, $\cw\lmn = \omega\lmn + i/\tau\lmn$.

@@

Although each model's fractional error is within 1\% of the perturbation theory result, each is dominated by systematic error due to the choice fitting ansatz.
For comparison, the same residual errors are shown in gray for the model presented in Ref.~\cite{Berti:2005ys}.

@@

    \State Define, $\mlam_{bulk}$, the bulk symbol space using the tensor-product of the power set of each basis symbol. This is the combined bulk for numerator and denominator symbols.
